\documentclass{cv}

\name{Sven Borer}
\address{中正區南昌路二段154號 台北市100}
\phone{(+886) 0933 45 85 40}
\email{sven.borer@gmail.com}
\homepage{https://svenborer.ch}
\github{svenborer}

\begin{document}
\begin{CJK*}{UTF8}{bsmi}

\maketitle%

\section{Personal \\ Interests}

I am interested in automation processes, maintaining computer systems, programming \& troubleshooting.

\section{Professional \\ Experience}

\subsection{Bank J. Safra Sarasin}[Basel, CH]
\begin{positions}
    \entry{IT System Engineer}{Aug 2010~--~Mar 2018}
\end{positions}
I worked for almost 8 years for an international private bank to administrate and build around 400 windows and some linux servers. My work included following tasks:

\begin{itemize}
    \item Managed multiple Microsoft Exchange Server Farms.
    \item Managed multiple Microsoft Servers, including Active Directory, File Services, DNS, SQL, etc.
    \item Managed complex automation tasks.
    \item Managed linux \& Windows servers, clusters and virtualized environments.
    \item Used powershell/python to write complex scripts to monitor \& administrating servers.
    \item Created web apps in a defined framework in order to manage servers and services.
    \item Involved in international rollouts.
    \item 3rd level support and incident management.
\end{itemize}

\section{Education}

\subsection{Bank Sarasin \& Cie AG}[Basel, CH]
\begin{positions}
    \entry{ICT System Engineer Trainee}{Aug 2006~--~Aug 2010}
\end{positions}

\section{Courses}
\subsection{National ChengChi University (國立政治大學)}[Taipei, TW]
\begin{positions}
    \entry{Mandarin Language Course}{May 2019~--~Dec 2019}
\end{positions}

\subsection{National Taiwan University (國立臺灣大學)}[Taipei, TW]
\begin{positions}
    \entry{Mandarin Language Course}{May 2018~--~Feb 2019}
\end{positions}

\section{Skills}

\begin{description}
  \item[Programming]
    \parbox[t]{\linegoal}{
      \strut%
      Powershell, Python, Bash, SQL, ASP.NET, Javascript, \LaTeX
      \strut%
    }
    \item[Services] Mail, AD, LDAP, DNS, SQL
    \item[OS] Windows Server, RedHat, CentOS, SLES 
    \item[Languages] German, English, Mandarin
\end{description}

\section{Certificates}
    \textbf{MCSA: Windows Server 2016} \printdate{2017} \\ 
    \hspace*{0.4cm}Exam 740: Installation, Storage and Compute with Windows Server 2016 \\
    \hspace*{0.4cm}Exam 741: Networking with Windows Server 2016 \\
    \hspace*{0.4cm}Exam 742: Identity with Windows Server 2016 \\
    \textbf{MCSE: Cloud Platform and Infrastructure} \printdate{2017} \\ 
    \hspace*{0.4cm}Exam 744: Securing Windows Server 2016 \\
\end{CJK*}
\end{document}
